04_DESeq_sexes

### 2019-08-28 analysis/04_DESeq2_sexes.Rmd
now with new color scheme from ggtext

```{r setup}

library(tidyverse)
library(DESeq2)
library(cowplot)
library(pheatmap)
library(viridis)
library(forcats)
library(caret) # LDA analysis
library(MASS) # LDA analysis

@@

```{r LDA}
# prep col data for LDA
colDataHyp <- subsetcolData2(c.colData, c("female_hypothalamus", "male_hypothalamus"))
colDataPit <- subsetcolData2(c.colData, c("female_pituitary", "male_pituitary"))
colDataGon <- subsetcolData2(c.colData, c("female_gonad", "male_gonad"))

@@

LDAplot.treatment(LDA.hyp1 , "Hypothalamus")
LDAplot.treatment(LDA.pit1 ,  "Pituitary")
LDAplot.treatment(LDA.gon1 , "Gonad")

@@

LDA.hyp1 <- LDAdata.hypothesis(vsd.hyp, colDataHyp)
LDA.pit1 <- LDAdata.hypothesis(vsd.pit, colDataPit)
LDA.gon1 <- LDAdata.hypothesis(vsd.gon, colDataGon)

LDAplot.hypothesis(LDA.hyp1 , "Hypothalamus")
LDAplot.hypothesis(LDA.pit1 ,  "Pituitary")
LDAplot.hypothesis(LDA.gon1 , "Gonad")
```

>>>>

```{r setup, include = FALSE}

library(tidyverse)
library(DESeq2)
library(cowplot)
library(pheatmap)
library(viridis)
library(forcats)
library(caret) # LDA analysis
library(MASS) # LDA analysis
library(ggtext) # for pretty plots

@@

```{r LDAdfs}
# prep col data for LDA
colDataHyp <- subsetcolData2(c.colData, c("female_hypothalamus", "male_hypothalamus"))
colDataPit <- subsetcolData2(c.colData, c("female_pituitary", "male_pituitary"))
colDataGon <- subsetcolData2(c.colData, c("female_gonad", "male_gonad"))

@@

@@

LDA.hyp2 <- LDAdata.hypothesis(vsd.hyp, colDataHyp)
LDA.pit2 <- LDAdata.hypothesis(vsd.pit, colDataPit)
LDA.gon2 <- LDAdata.hypothesis(vsd.gon, colDataGon)

```

```{r LDA, fig.width = 9}

# figures for both of the above

# treatment
a <- LDAplot.treatment(LDA.hyp1 , "Hypothalamus model 1", "parental state ~ .  0.277 pred. acc.",
                        "LD1, F = 7.1504779", "LD2, F = 2.4219585")

b <- LDAplot.treatment(LDA.pit1 ,  "Pituitary model 1", "parental state ~ .  0.405 pred. acc.",
                        "LD1, F = 9.6144160", "LD2, F = 3.7773314")

c <- LDAplot.treatment(LDA.gon1 , "Gonad model 1", "parental state ~ .  has 0.297 pred. acc.",
                        "LD1, F = 6.137500", "LD2, F = 3.320437")

c <- c + theme(legend.direction = "horizontal")
mylegend <- get_legend(c)

temp <- plot_grid(a + theme(legend.position = "none"),
                  b + theme(legend.position = "none"),
                  c + theme(legend.position = "none"), nrow = 1)

plot_grid(temp, mylegend, nrow = 2, rel_heights = c(1,0.3))

# hypothesis

d <- LDAplot.hypothesis(LDA.hyp2 , "Hypothalamus model 2", "parental stage ~ .  0.432 pred. acc.",
                        "LD1, F = 7.386458", "LD2, F = 3.720794")

e <- LDAplot.hypothesis(LDA.pit2 ,  "Pituitary model 2", "parental stage ~ .  0.473 pred. acc.",
                        "LD1, F = 7.846659", "LD2, F = 5.076861")

f <- LDAplot.hypothesis(LDA.gon2 , "Gonad model 3", "parental stage ~ .  has 0.368 pred. acc.",
                        "LD1, F = 6.029069", "LD2, F = 3.837591")

f <- f + theme(legend.direction = "horizontal")
mylegend <- get_legend(f)

temp <- plot_grid(d + theme(legend.position = "none"),
                  e + theme(legend.position = "none"),
                  f + theme(legend.position = "none"), nrow = 1)

plot_grid(temp, mylegend, nrow = 2, rel_heights = c(1,0.3))
```
